CommonMind Consortium: DLPFC

### 2020-09-21 combined_analysis/diff.networks.Rmd
Update diff networks

```{r plot.enrich.Dx, fig.width=9}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx, module, 8) + ggtitle(module)
	})    
plot_grid(plotlist = figList, ncol=1)
```

@@

## Discovery cohort
```{r plot.discovery.Dx_Sex}
# plot discovery and testing.  
ggplot(df_test.Dx_Sex, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

>>>>

```{r plot.enrich.Dx, fig.width=9, fig.height=25}
figList = lapply( df_cohort2$Module[i], function(module){
	plot_enrich(df_module_enrich.Dx, module, 8) + ggtitle(module)
	})    
plot_grid(plotlist = figList, ncol=1)
```

@@

## Discovery cohort
```{r plot.discovery.Dx_Sex}
# plot discovery and testing.  
ggplot(df_test.Dx_Sex, aes(Module, -log10(P.Value))) + geom_bar(stat='identity', fill=df_test.Dx_Sex$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~P)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

stat = sapply(1:1000, function(i){

	set.seed(i)
	n = 1000
	p = 40
	X = matrix(rnorm(n*p), n,p)
	Y = matrix(rnorm(n*p), n,p)

	stat = sLED:::sLEDTestStat(D, rho=1)$stats
	max(0, stat)
})

fit = egamma( stat )

fit$parameters
